---
title: "Assignment 12"
author: "Nolan Blake"
date: "2023-04-02"
output: html_document
---

------------------------------------------------------------------------

### ***Objective***

clean and Reorganize a Data Set 

------------------------------------------------------------------------

### ***Set Working Directory***

```{r}
setwd("C:/Users/Nolan/Documents/USF Assignment Archive/2023 Spring/Visual Analitics")

```

### ***Load needed Libraries***

```{r}

library(readr)

```

### ***Load data***

Make sure that the data is in a usable format Website here -\> <http://www2.census.gov/programs-surveys/popest/tables/2010-2011/state/totals/nst-est2011-01.csv>

```{r}

readURL<-"http://www2.census.gov/programs-surveys/popest/tables/2010-2011/state/totals/nst-est2011-01.csv"
  dfPopulation <- read.csv(url(readURL))
  dfPopulationv2<-as.data.frame(dfPopulation)
  
  
```

### ***Start cleaning/Get rid of useless rows***

These couple of rows are just descriptions and are not usable for anything useful

```{r}
dfPopulationv2 <- dfPopulationv2[-1:-8,]
dfPopulationv2 <- dfPopulationv2[-52:-58,]

dfPopulationv2$stateName <- dfPopulationv2[,1]
dfPopulationv2<-dfPopulationv2[,-1]

#dfPopulationv2 <- dfPopulationv2[,-:-8]
dfPopulationv2<-dfPopulationv2[,-5:-9]

```

### ***Rename the columns to something more useful***

```{r}
Topnames <-c("Census", "Estimate", "Pop2010", "Pop2011","StateName")
colnames(dfPopulationv2) <-Topnames
```

### ***finish cleaning***

make the row classes representative of whatthey are and get rid of unnecessary symbols print it out to make sure that it looks correct

```{r}
dfPopulationv2$Census<-as.numeric(gsub(",","",dfPopulationv2$Census))
dfPopulationv2$Estimate<-as.numeric(gsub(",","",dfPopulationv2$Estimate))
dfPopulationv2$Pop2010<-as.numeric(gsub(",","",dfPopulationv2$Pop2010))
dfPopulationv2$Pop2011<-as.numeric(gsub(",","",dfPopulationv2$Pop2011))
dfPopulationv2$StateName <- gsub("\\.",'',dfPopulationv2$StateName)

dfPopulationv2
```
